SBML L3 paper response to reviewers

### 2020-01-13 main.tex
Further edits

We thank you for reviewing our manuscript on SBML Level~3 and providing many thoughtful comments and suggestions.  They helped us improve the manuscript.  Below you will find a point-by-point explanation of our responses to the reviewer's points; in addition, we have include a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional corrections and updates beyond the changes in response to the reviewer comments.

>>>>

We thank you for reviewing our manuscript on SBML Level~3 and providing many thoughtful comments and suggestions.  They helped us improve the manuscript.

Included below is a point-by-point explanation of our responses to the reviewer's comments; in addition, we have also included a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional minor corrections and updates beyond the changes made for reviewer feedback, which we have done in an effort to improve the manuscript further (for example, by reducing the overall number of citations and improving overall text cohesion).
